### 2024-09-06 texts/paper_closing.tex
more minor improvements

% Created 2024-09-06 vr 16:21
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

While private museums are thus generally characterized as fragile, it is not always clear in relation to whom.
Among the most explicit is \textcite{Walker_2019_collector}, who characterizes public institutions as relatively stable (which constitutes the reason why private collectors aim to form cooperations with them); \textcite{Bechtler_Imhof_2018_future} implicitly also highlight the longevity of state-run institutions.
However, no systematic data is used to estimate public museum longevity, and while some
remarks are made that public spending cuts might result in problems for public museum operations (p.233), the overall characterization of them remains as immortal \parencite{Frey_Meier_2002_beyeler}.
Responsible for the characterization of private museums as fragile might also be implicit reliance on the ICOM definition \parencite{ICOM_2024_definition} of museums as "permanent institutions" (according to which every closing is indicative of fragility), which is echoed by an interviewee of \textcite{Walker_2019_collector} who expresses (his perspective on) the prevalent perspective as "We assume museums are forever" (p.235).
So far a third comparison has been absent, namely that to other non-profit museums which are not initiated and run by a single collector, but by a wider group of founders, foundations or associations.
As these share with private museums a common organizational form of the non-profit organization or foundation  and the same harsh environment of the cultural sector where operations cannot sustain an organization, yet differ primarily in regards to their diversification, i.e. their reliance on a single founder as central authority and income stream, they provide a effective way of investigating the effect of diversification on museum survival.

@@

While the low diversification, i.e. the centrality of the founder for museum finances, has been argued to constitute the key feature of private museum vulnerability, it is also important to consider the other ways in which private museums, as (non-profit) organizations, are entangled with their environments.
Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations are likely factors that contribute to its viability and hence longevity.
While some of these aspects can be influenced by the founder (in particular the museum's location and strategies) , other are less so.
In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
\paragraph*{Competition}

mechanism: losing motivation?

@@

Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
Next to "hard" organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate. 
However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity as "anything goes" and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.

@@

A newly constructed database, assembled from different sources, is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
Currently, the database includes 548 museums (of which 451 are currently open, the remainder having closed or transformed into other organizational forms).
Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of the each institution with museum-year as the unit of analysis.
This data allows to conduct survival analysis (also known as event history analysis), the most common statistical technique to investigate hazard rates and identify mortality-assocated covariates \parencite{Moore_2015_survival,Allison_2014_event}.

@@

\bigbreak
\noindent
A number of control variables are used: 
On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
Women constitute a minority of the private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would have a greater difficulties in securing resources third parties, presumably primarily governments and corporate sponsors.
However, women may also be particularly associated with philanthropic initiatives (unlike e.g. corporate activities, \cite{Milam_2013_artgirls}) to such an extent that devaluation of female initiatives may not necessarily be present.

Centrality of the founder's vision is measured via the proxy of whether the name of the founder is included in the name of the museum.

@@

In total, 523 private museums are included in the dataset which are either open or have closed\footnote{This does not include 25 institutions which were private museums at some point and have since been transformed into other organizational forms; these cases are discussed in the limitations.}.
While around 20\% of private museums have opened before 2000, the retrospective data collection does not rule out the possibility that some institutions were missed, with such risks likely being higher for earlier time periods.
To ensure that the effect of such missed museums is does not distort insights, the time range in question is limited to events between 2000-2021.
A small number of museums are excluded, in particular three museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), as well as two which closed before 2000 as they fall outside the period under investigation.
This leaves 503 private museums at risk, of which 68 have closed.
6096 museum-years are observed; table \ref{tbl:t_sumstats} shows summary statistics for all variables.
\subsubsection*{Calendar Year hazard}

@@

While typically in survival analysis closing risk is seen as a function of age, previous studies have not done so, instead focusing on average yearly closing rates.
To ensure comparability with these, I first analyze closing rates the same, and discuss age-related closing rate below.
Summary yearly closing results in an average closing rate of 0.84\%; i.e. on average each year 0.84\% of the private museum population closes (weighing the yearly mortality rate by number of museums at risk results in an estimate of 1.12\%).
It is worth pointing out however that closing rates appear to vary substantially over time (figure \ref{fig:p_hazard_time}); with an average closing rate of 0.21\% from 2000 to 2010 (with only 4 closures taking place in that time period), and a rate of 1.36\% from 2010 onwards.

@@

While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})\footnote{IRS data is not without limitations, such as only being required from larger organizations, misreporting, and the difficulty of inferring closing from non-filing. Nevertheless, it constitutes the most fine-grained data source to investigate non-profit survival}.
None of these focus on art museums exclusively (\textcite{Hager_2001_vulnerability} focuses on Art NPOs, \textcite{Bowen_etal_1994_charitable} and \textcite{Gordon_etal_2013_insolvency} on NPOs generally), but report survival estimates by organizational form, including museums.
\textcite{Bowen_etal_1994_charitable} investigates the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
\textcite{Gordon_etal_2013_insolvency} observes 35 closures over the years of 2000-2003 with 5,167 museum-years (p.368), resulting in an average annual closing rate of 0.68\% (p.377).
Some of this difference may be explained by higher shares of smaller organizations in \textcite{Bowen_etal_1994_charitable}, where museums of any size are included, whereas \textcite{Gordon_etal_2013_insolvency} excluded NPOs with operational revenues below 150,000 USD by, as smaller non-profits are at higher risk of closing \parencite{Harrison_Laincz_2008_nonprofit,Helmig_Ingerfurth_Pinz_2013_nonprofit}.

Focusing directly on Art museums, rather than museum generally as part of the wider focus on Art NPOs, \textcite{Hager_2001_vulnerability} observes 42 closures over a period of 4 years (1994-1997) from a starting populaton of 448 (p.383).
As his way of delineating the population (having "filed an annual Form 990 tax return with the IRS for the 1990, 1991, or 1992 tax year", p.380) does not rule out that some closings took place in 1991, 1992 or 1993\footnote{In particular it is unclear why 1993 is not treated as belonging to the observation period}, attributing some closings to these years is likely appropriate, and presumably roughly equivalent to assuming an observation period of five (rather than four) years, which corresponds to an average yearly closing rate of \(1-(406/448)^{1/5}\) = 1.9\%.\footnote{So far it is hard to tell why art museums appear to have higher closing rates than museums generally.
According to the \textcite{IMLS_2008_funding}, art museums have above-average reliance on earned income (46.1\% compared to 43.7\% on average, p.26), and \textcite{Bowen_etal_1994_charitable} argue that a higher reliance on income is associated with higher exit rates (p.102), but it is questionable whether such an a small difference in percent earned can explain a 1.7-2.7 times higher closing risk.
Similarly, while art museums do not have the largest coffers (in particular museums of natural history and science are substantially larger \parencite{IMLS_2008_funding,Bowen_etal_1994_charitable}), art museums have substantially higher incomes than the history museums (which are more frequent), historical societies and botanical gardens \parencite{IMLS_2008_funding} as well as "other museums" with more specialized and/or local focuses \parencite{Bowen_etal_1994_charitable}.
Especially the larger number of history museums, and the more restrictive inclusion by \textcite{Hager_2001_vulnerability} in comparison to \textcite{Bowen_etal_1994_charitable} make the higher mortality rate for art museums than museums generally puzzling.}

@@

Next to average yearly closing rates, private museum closing can also be investigated over its age (no comparison to previous studies can be done these did not report age-dependent mortality estimates).
Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
The hazard rate increases strongly from 0.10\% in the first two years, to 0.69\% in the first 5 years, to 1.20\% at year 8, around which it then fluctuates, leading to an average hazard of 1.16\% for the first 30 years. \footnote{While it is possible to calculate the average hazard over longer periods (e.g. the overall average hazard rate is 0.90\%), for ages above 30 only few observations are available, which make these predictions rather uncertain.}
The increase in the first years is likely explained by the fact that as the establishment of a museum requires considerable resources, their founders have allocated enough resources to keep the risk of closure minimal in the first years after opening.

@@

The reputation of the founder is not statistically related to closure. 
Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (21\% elevated closing risk) and by founders who were included at some point but are no longer included (58\% elevated closing risk), however none of the differences are statistically significant.
It is also worth to point out that the order of the categories does not fully correspond to the expected order, according to which museums whose collectors are not included would be more likely to close than collectors who are.
However, as all differences are not statistically significant, there is no strong evidence that this reflects unexpected status mechanisms rather than randomness.
it nevertheless provides some evidence that status matters; as in particular the loss of status appears to be substantially associated with museum closure.

Museums whose name contain the name of the founder face a non-significantly 4.9\% elevated risk of closure, which indicates that there is little evidence that founders face greater difficulties to secure a long-term future for their museums by choosing to emphasize their personal contribution.
It might have been expected that such central positioning of the founder might limit longevity by disincentivizing contributions by other parties.
However, as the direct mechanism of declining contributions cannot be observed, its absence cannot be assumed either.
It might be the case that other parties do indeed feel less inclined to contribute but that these gaps are filled by a stronger commitment of the founder, who having committed her name to the enterprise, wants to keep her museum open event at great costs.
\subparagraph*{founder conclusion}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_popprxcnt.pdf}
\caption{\label{fig:p_pred_popprxcnt}Predicted Avg. Hazard Rate on Regional PM Density and Population}
\end{figure}

@@

At the local level, the number of private museum and population numbers predict survival chances as the main effects of population and number of private museums as well as its interaction are significant.
The particular pattern is complex:
As both main terms are positive and the interaction negative, at low values increases in either variable are associated with increases in mortality (figure \ref{fig:p_condmef}).
Thus, for population values of 0 to 2.97 million people, an increase in the number of private museums corresponds to an increase in mortality (bottom half of figure \ref{fig:p_pred_heatmap}), which provides support for the view that competition leads to museum closure, in particular as this range includes 5056 museums years, or 83\% of the dataset. 
Yet at the same time, at low private museums numbers (0 to 3 private museums), increases in population also increase mortality; this range also includes a large number of museum-years (4960 museum years; 81\% of the data).
Such a relationship is unexpected insofar as it is unclear why a larger potential audience would be associated with a higher risk of closure.\footnote{Alternative approaches of modeling competition are discussed in the supplementary materials, but cannot answer this question.}
A possible explanation might be that collectors in less densely populated areas are more committed than those in less populated areas precisely because they know they cannot count visitors to contribute substantially.
Alternatively, areas with high population and low private museum numbers might more generally lack cultural infrastructure; which one could see supported by closures in Jakarta, Istanbul and Mexico City, but less so by closings in Paris, Tokyo or Madrid.
Low private museums indicating lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
More in line with expectation is however the association between increases of population numbers and lower mortality at higher numbers of private museums (right half), as it indicates that audiences can facilitate museum survival.

@@

While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, number of private museums in the local surrounding, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition.
\paragraph*{Identity Variables}

>>>>

% Created 2024-09-06 vr 17:50
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

While private museums are thus generally characterized as fragile, it is not always clear in relation to whom.
Among the most explicit is \textcite{Walker_2019_collector}, who characterizes public institutions as relatively stable (which constitutes the reason why private collectors aim to form cooperations with them); \textcite{Bechtler_Imhof_2018_future} implicitly also highlight the longevity of state-run institutions.
However, no systematic data is used to estimate public museum longevity, and while some
remarks are made that public spending cuts might result in problems for public museum operations (p.233), the overall characterization of them remains as immortal \parencite{Frey_Meier_2002_beyeler}.
Responsible for the characterization of private museums as fragile might also be implicit reliance on the ICOM definition \parencite{ICOM_2024_definition} of museums as "permanent institutions" (according to which every closing is indicative of fragility), which is echoed by an interviewee of \textcite{Walker_2019_collector} who expresses (his perspective on) the prevalent perspective as "we assume museums are forever" (p.235).
So far a third comparison has been absent, namely that to other non-profit museums which are not initiated and run by a single collector, but by a wider group of founders, foundations or associations.
As these share with private museums a common organizational form of the non-profit organization or foundation  and the same harsh environment of the cultural sector where operations cannot sustain an organization, yet differ primarily in regards to their diversification, i.e. their reliance on a single founder as central authority and income stream, they provide a effective way of investigating the effect of diversification on museum survival.

@@

While the low diversification, i.e. the centrality of the founder for museum finances, has been argued to constitute the key feature of private museum vulnerability, it is also important to consider the other ways in which private museums, as (non-profit) organizations, are entangled with their environments.
Its ability to attract audiences, which may involve competition with other museums, secure cooperations with other museums, acquire sponsorships from cooperations and fundings from governments and other foundations possibly constitute factors that contribute to its viability and hence longevity.
While some of these aspects can be influenced by the founder (in particular the museum's location and strategies) , other are less so.
In particular when they rely on the decision-making of other art-field actors, such as competition with other museums and sponsorship/funding choices, the influence of the individual founder is severely limited.
\paragraph*{Competition}

@@

Legitimacy might be obtained by isomorphism, i.e. adopting features associated with blueprints \parencite{diMaggio_1983_iron}.
Next to material organizational features, adherence to naming conventions has been found to enhance legitimacy \parencite{Glynn_Abzug_2002_names}; organizations that adhere to field norms about name length, name ambiguity (usage of artificial names) and name domain specificity (mentioning industry) were judged more legitimate. 
However, the category of museums could be relatively flexible (for example, the term "museum" is generally not subject to state regulation in the US or Germany \parencite{Museumsbund_ICOMDE_2006_standards,Lister_2023_marketing}), which might result in a relatively high tolerance of diversity and hence limited devaluation of non-conforming, atypical members \parencite{Bogaert_etal_2014_ecological}.

@@

A newly constructed database, assembled from different sources, is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
Currently, the database includes 548 museums (of which 451 are currently open, the remainder having closed or transformed into other organizational forms).
Using this database, in particular year of opening and, if available, closing, it is possible to reconstruct the life course of the each institution with museum-year as the unit of analysis.
While around 20\% of private museums have opened before 2000, the retrospective data collection does not rule out the possibility that some institutions were missed, with such risks likely being higher for earlier time periods.
To ensure that the effect of such missed museums is does not distort insights, the time range in question is limited to events between 2000-2021.
This data allows to conduct survival analysis (also known as event history analysis), the most common statistical technique to investigate hazard rates and identify mortality-assocated covariates \parencite{Moore_2015_survival,Allison_2014_event}.

@@

\bigbreak
\noindent
A number of control variables are used: 
On the level of the founder, gender constitutes a time-invariant variable; with possible values being male, female and couple.
Women constitute a minority of the private museums founders, thus from a typicality perspective \parencite{Rosch_1975_family} museums by female founders would be expected to close more often as female founders would have a greater difficulties in securing resources third parties, presumably primarily governments and corporate sponsors.
However, women may also be particularly associated with philanthropic initiatives - in contrast to corporate activities \parencite{Milam_2013_artgirls} - to such an extent that devaluation of female initiatives may not necessarily be present.

@@

In total, 523 private museums are included in the dataset which are either open or have closed\footnote{This does not include 25 institutions which were private museums at some point and have since been transformed into other organizational forms; these cases are discussed in the limitations.}.
A small number of museums are excluded, in particular three museums for which the closing date could not be found, 15 museums which opened in 2021 and later (as survival analyses requires positive survival times), as well as two which closed before 2000 as they fall outside the period under investigation.
This leaves 503 private museums at risk, of which 68 have closed.
6096 museum-years are observed; table \ref{tbl:t_sumstats} shows summary statistics for all variables.
\subsubsection*{Comparing private museum hazard rates to previous studies}

@@

While typically in survival analysis closing risk is seen as a function of age, previous studies have not done so, instead focusing on average yearly closing rates.
To ensure comparability with these, I first analyze closing rates the same, and discuss age-related closing rate below.
Summarizing yearly closing proportions results in an average closing rate of 0.84\%; i.e. on average each year 0.84\% of the private museum population closes (weighing the yearly mortality rate by number of museums at risk results in an estimate of 1.12\%).
It is worth pointing out however that closing rates appear to vary substantially over time (figure \ref{fig:p_hazard_time}); with an average closing rate of 0.21\% from 2000 to 2010 (with only 4 closures taking place in that time period), and a rate of 1.36\% from 2010 onwards.

@@

While I did not find a systematic literature review or meta-analysis, a number of individual studies had investigated similar populations based on IRS data (see table \ref{tbl:litreview})\footnote{IRS data is not without limitations, such as only being required from larger organizations, misreporting, and the difficulty of inferring closing from non-filing. Nevertheless, it constitutes the most fine-grained data source to investigate non-profit survival}.
None of these focus on art museums exclusively (\textcite{Hager_2001_vulnerability} focuses on Art NPOs, \textcite{Bowen_etal_1994_charitable} and \textcite{Gordon_etal_2013_insolvency} on NPOs generally), but report survival estimates by organizational form, including museums.
\textcite{Bowen_etal_1994_charitable} investigates the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
\textcite{Gordon_etal_2013_insolvency} observes 35 closures over the years of 2000-2003 with 5,167 museum-years (p.368), resulting in an average annual closing rate of 0.68\% (p.377).
Some of this difference may be explained by higher shares of smaller organizations in \textcite{Bowen_etal_1994_charitable}, where museums of any size are included, whereas \textcite{Gordon_etal_2013_insolvency} excluded NPOs with operational revenues below 150,000 USD, as smaller non-profits are at higher risk of closing \parencite{Harrison_Laincz_2008_nonprofit,Helmig_Ingerfurth_Pinz_2013_nonprofit}.

Focusing directly on Art museums, rather than museum generally as part of the wider focus on Art NPOs, \textcite{Hager_2001_vulnerability} observes 42 closures over a period of 4 years (1994-1997) from a starting populaton of 448 (p.383).
As his way of delineating the population (having "filed an annual Form 990 tax return with the IRS for the 1990, 1991, or 1992 tax year", p.380) does not rule out that some closings took place in 1991, 1992 or 1993\footnote{In particular it is unclear why 1993 is not treated as belonging to the observation period}, attributing some closings to these years is likely appropriate, and presumably roughly equivalent to assuming an observation period of five (rather than four) years, which corresponds to an average yearly closing rate of 1.9\%.\footnote{So far it is hard to tell why art museums appear to have higher closing rates than museums generally.
According to the \textcite{IMLS_2008_funding}, art museums have above-average reliance on earned income (46.1\% compared to 43.7\% on average, p.26), and \textcite{Bowen_etal_1994_charitable} argue that a higher reliance on income is associated with higher exit rates (p.102), but it is questionable whether such an a small difference in percent earned can explain a 1.7-2.7 times higher closing risk.
Similarly, while art museums do not have the largest coffers (in particular museums of natural history and science are substantially larger \parencite{IMLS_2008_funding,Bowen_etal_1994_charitable}), art museums have substantially higher incomes than the history museums (which are more frequent), historical societies and botanical gardens \parencite{IMLS_2008_funding} as well as "other museums" with more specialized and/or local focuses \parencite{Bowen_etal_1994_charitable}.
Especially the larger number of history museums, and the more restrictive inclusion by \textcite{Hager_2001_vulnerability} in comparison to \textcite{Bowen_etal_1994_charitable} make the higher mortality rate for art museums than museums generally puzzling.}

@@

Next to average yearly closing rates, private museum closing can also be investigated over its age (no comparison to previous studies can be done these did not report age-dependent mortality estimates).
Figure \ref{fig:p_hazard} shows the hazard rate over time, figure \ref{fig:p_surv} the corresponding survival probability.
The hazard rate increases strongly from 0.10\% in the first two years, to 0.69\% in the first 5 years, to 1.20\% at year 8, around which it then fluctuates, leading to an average hazard of 1.16\% for the first 30 years\footnote{While it is possible to calculate the average hazard over longer periods (e.g. the overall average hazard rate is 0.90\%), for ages above 30 only few observations are available, which make these predictions rather uncertain.}.
The increase in the first years is likely explained by the fact that as the establishment of a museum requires considerable resources, their founders have allocated enough resources to keep the risk of closure minimal in the first years after opening.

@@

Other founder-level characteristics also do not indicate that founder-related variables are strongly associated to museum closure, as the coefficients of ARTnews ranking inclusion (measuring reputation) and inclusion of founder's name in the museum name are not statistically significant.
Museums whose founders are not included in the ARTnews collector ranking (reference category) are the least likely to close, followed by museums whose founders are included (21\% elevated closing risk) and by founders who were included at some point but are no longer included (58\% elevated closing risk), however none of the differences are statistically significant.
It is also worth to point out that the order of the categories does not fully correspond to the expected order, according to which museums whose collectors are not included would be more likely to close than collectors who are.
However, as all differences are not statistically significant, there is no strong evidence that this reflects unexpected status mechanisms rather than randomness.

@@

@@

At the local level, the number of private museum and population numbers predict survival chances as the main effects of population and number of private museums as well as its interaction are significant.
The particular pattern is complex:
As both main terms are positive and the interaction negative, at low values increases in either variable are associated with increases in mortality (figure \ref{fig:p_condmef}).
Thus, for population values of 0 to 2.97 million people, an increase in the number of private museums corresponds to an increase in mortality (bottom half of figure \ref{fig:p_pred_heatmap}), which provides support for the view that competition leads to museum closure, in particular as this range includes 5056 museums years, or 83\% of the dataset. 
Yet at the same time, at low private museums numbers (0 to 3 private museums), increases in population also increase mortality; this range also includes a large number of museum-years (4960 museum years; 81\% of the data).
Such a relationship is unexpected insofar as it is unclear why a larger potential audience would be associated with a higher risk of closure.\footnote{Alternative approaches of modeling competition are discussed in the supplementary materials, but cannot answer this question.}
A possible explanation might be that collectors in less densely populated areas are more committed than those in less populated areas precisely because they know they cannot count visitors to contribute substantially.
Alternatively, areas with high population and low private museum numbers might more generally lack cultural infrastructure; which one could see supported by closures in Jakarta, Istanbul and Mexico City, but less so by closings in Paris, Tokyo or Madrid.
However, low private museums indicating lack of cultural infrastructure might also explain the decrease in mortality associated with increases in private museum numbers at high population values (figure \ref{fig:p_pred_heatmap}, upper half), as such pattern does not correspond to that predicted by competition.
More in line with expectation is however the association between increases of population numbers and lower mortality at higher numbers of private museums (right half), as it indicates that audiences can facilitate museum survival.

@@

While not all associations correspond to predictions made by resource dependence, the most direct measurement of increased competition, number of private museums in the local surrounding, is associated with higher closing chances for a large part of the sample, which in turn supports the substantial role of competition (H3).
\paragraph*{Identity Variables}
